### 2019-03-19 2_metg.tex
Update METG result for MPI.

METG is thus the result of drawing a vertical line through
Figure~\ref{fig:efficiency-mpi} at the desired level of efficiency,
and taking the intersection of this line with the task granularity
curve. In the figures, the red, dashed line shows the 50\% efficiency
level. At 50\% efficiency, MPI achieves an average task granularity of
4.5 us, thus the METG(50\%) of MPI is 4.5 us for this configuration of
the application. The number 50\% is chosen arbitrarily, but is a
reasonable choice for this application because it represents a point
at which many systems will have plateaued, yet the overall efficiency
is still reasonable. Lower values would likely not be reasonable,
because in most cases operators of computing facilities prefer to
maintain higher levels of utilization of the machines. And higher
values risks misrepresenting the performance of some systems (not
shown in the figures above).

>>>>

METG is thus the result of drawing a vertical line through
Figure~\ref{fig:efficiency-mpi} at the desired level of efficiency,
and taking the intersection of this line with the task granularity
curve. In the figures, the red, dashed line shows the 50\% efficiency
level. At 50\% efficiency, MPI achieves an average task granularity of
4.6 us, thus the METG(50\%) of MPI is 4.6 us for this configuration of
the application. The number 50\% is chosen arbitrarily, but is a
reasonable choice for this application because it represents a point
at which many systems will have plateaued, yet the overall efficiency
is still reasonable. Lower values would likely not be reasonable,
because in most cases operators of computing facilities prefer to
maintain higher levels of utilization of the machines. And higher
values risks misrepresenting the performance of some systems (not
shown in the figures above).
